The Tor Network - Design and Defenses \\ \Large Computer Security 1 - CS5460 \\ \LaTeX{}

### 2013-12-06 paper.tex
various improvements

The client first establishes a TLS connection with the first relay, $R_{1}$, using the relay's public key. The client then uses a single Diffie-Hellman-Merkle key exchange to negotiate $K_{1}$ which is then used to generate two symmetric keys: a forward key $K_{1,F}$ and a backwards key $K_{1,B}$. $K_{1,F}$ is used to encrypt all communication from the client to $R_{1}$ and $K_{1,B}$ is used for all replies from $R_{1}$ to the client. These keys are used conjunction with the symmetric cipher suite negotiated during the TLS handshake, thus forming an encrypted tunnel. Once this one-hop circuit has been created, the client then sends $R_{1}$ the RELAY\_EXTEND command, the address of $R_{2}$, and the client's half of the Diffie-Hellman-Merkle protocol ($ g^a mod b $) using $K_{1,F}$. $R_{1}$ performs a TLS handshake with R${2}$ and uses $R_{2}$'s public key to send $ g^a mod b $ to $R_{2}$, who replies with his half of the handshake and a hash of $K_{2}$. $R_{1}$ then forwards this to the client under $R_{1,B}$ with the RELAY\_EXTENDED command to notify the client. The client generates $K_{1,F}$ and $K_{1,B}$ from $K_{2}$, and repeats the process for $R_{3}$,\cite{Ling2012} as shown in Figure 3.

@@

Encryption is a necessary component for privacy within the Tor network. Traffic passing between nodes must be secured from outsiders, and even compromised nodes must not be able to observe the traffic in cleartext. Privacy is also important for traffic outside the network; encrypted connections between the exit node and the target web server must also be achieved. Furthermore, two layers are needed: one for inside the network and one for outside it.

Within the network, nodes talk to each other via the Transport Security Layer (TLS) protocol. When a circuit is built, each pair of nodes within it must first come to an agreement over an encryption key and the specific cipher to use for encryption. There are several mechanisms by which this can be done, all of which use Diffie-Hellman (DH) for key exchange. The most common methods include: TLS\_RSA, which rely upon public and private keys generated with RSA; TLS\_DHE, ephemeral DH; TLS\_ECDH, DH based on elliptic curves, and TLS\_ECDHE, ephemeral elliptic curve DH. It should be noted that only TLS\_DHE and TLS\_ECDHE provide perfect forward secrecy, so it is no surprise that Tor exclusively prefers them. Once encryption keys and the specific cipher (as well as its mode) have been agreed upon, communication of traffic between two nodes can be encrypted and exchanged.

% http://security.stackexchange.com/questions/8343/what-key-exchange-mechanism-should-be-used-in-tls
% https://en.wikipedia.org/wiki/Comparison_of_TLS_implementations
% https://www.ipa.go.jp/security/rfc/RFC5246-ACJA.html
% 4134 -- 0x0039 TLS_DHE_RSA - the key exchange is an ephemeral Diffie-Hellman: the server dynamically generates a DH public key and sends it to the client; the server also signs what it sends. For DHE_RSA, the server public key must be of type RSA, and its certificate must be appropriate for signatures (the Key Usage extension, if present, must include the digitalSignature flag).
% 5566 -- 0xc013 TLS_ECDHE_RSA - the server sends a dynamically generated (ephemeral?) EC Diffie-Hellman key, and signs it with its own RSA key.

Tor users typically use the Tor Browser Bundle, (TBB) a custom build of Mozilla Firefox with a focus on security and pricacy. The TBB not only provides special handling of client-side scripts such as Javascript, but also offers the HTTPS Everywhere extension, which uses regular expressions to rewrite web requests into ones that use HTTPS. Thus, if the web server is capable of handling SSL or TLS connections, HTTP communications will be encrypted under them. Like any typical browser, the TBB negotiates with the web server for the cipher and keys required for SSL/TSL, except that this negotiation entirely occurs through the Tor circuit. As previously noted, this information, along with subsequent HTTP data, is encrypted between each node in the circuit. During transmission, each node in the circuit decrypts its layer in turn, until the final node (the exit) passes the data to the target server. The TLS/IP connections remain open, so the returned information likewise travels back up the circuit to the end user.

In September 2013, Robert Graham of Errata Security analyzed 22,920 incoming connections to his exit node and found that 89.9\% of the circuits agreed to use the Advanced Encryption Standard (AES) block cipher in cipher-block chaining (CBC) mode. This is the most common mode for AES, and allows for parallel decryption of the data blocks. The other 10.1\% of the circuits relied upon three rounds of the Data Encryption Standard (triple DES) cipher for encryption. Furthermore, 75.7\% of the circuits used elliptic-curve DH, with the remaining 22.3\% relying upon traditional RSA DH.\cite{Graham2013} Both protocols are discussed below.

@@

RSA is an algorithm for public-key cryptography. Its security is based on the infeasibility of factoring the product of two large primes. RSA, like all other public-key cryptography algorithms, relies upon two keys: one public and the other private. The public key may be published and is used for encryption and for the verification of digital signatures. The private key is used for decryption and the generation of digital signatures. Thus, only the owner of the private key can decrypt incoming messages, and only they can digitally sign outbound messages. These properties make RSA and other public-key algorithms extremely powerful as they provide authenticity, integrity, and privacy of communications between two parties.

Tor version 2.3.x and previous rely upon TLS\_DHE for the key exchange mechanism. Per the TLS specification, the server generates a Diffie-Hellman public key and sends it to the client. The server also uses its RSA private key to sign everything that it sends to the client during the DH exchange. The client can then confirm the digital signature to verify the authenticity of the communication from the Tor relay.

@@

A smaller key size is one of the most significant benefits introduced by ECC. Current NIST recommendations state that a key size of 160 bits for ECC offers a similar level of security to 1024 bits of RSA/DH. Likewise, 224 bits for ECC is analogous to 2048 bits of RSA/DH. It should be noted that the required key sizes for ECC increases significantly slower than the key sizes for RSA and Diffie-Hellman. Thus ECC offers more security per increase in key size than for RSA. The smaller key size also directly correlates to an increase in computational efficiency; as the bit size increases, the speed difference between Diffie-Hellman and ECC grows superlinearly.\cite{CaseForECC}

Tor is currently undergoing a transition from RSA-based to elliptic-curve-based TLS. Tor 2.4.x introduced TLS\_ECDHE, which uses an elliptic-curve variant of the Diffie-Hellman key exchange. Like TLS\_DHE, the server uses its RSA key to digitally signs communication to the client. The TLS\_ECDHE protocol is believed to be more secure than TLS\_DHE.

@@

Once the SSL/TLS handshake completes, both parties use the generated session key and turn to symmetric-key encryption for hiding of data. Common symmetric-key algorithms include Data Encryption Standard, Advanced Encryption Standard, and RC4.

@@

>>>>

The client first establishes a TLS connection with the first relay, $R_{1}$, using the relay's public key. The client then uses a single Diffie-Hellman-Merkle key exchange to negotiate $K_{1}$ which is then used to generate two symmetric keys: a forward key $K_{1,F}$ and a backwards key $K_{1,B}$. $K_{1,F}$ is used to encrypt all communication from the client to $R_{1}$ and $K_{1,B}$ is used for all replies from $R_{1}$ to the client. These keys are used conjunction with the symmetric cipher suite negotiated during the TLS handshake, thus forming an encrypted tunnel. Once this one-hop circuit has been created, the client then sends $R_{1}$ the RELAY\_EXTEND command, the address of $R_{2}$, and the client's half of the Diffie-Hellman-Merkle protocol ($ g^a mod b $) using $K_{1,F}$. $R_{1}$ performs a TLS handshake with R${2}$ and uses $R_{2}$'s public key to send $ g^a mod b $ to $R_{2}$, who replies with his half of the handshake and a hash of $K_{2}$. $R_{1}$ then forwards this to the client under $R_{1,B}$ with the RELAY\_EXTENDED command to notify the client. The client generates $K_{1,F}$ and $K_{1,B}$ from $K_{2}$, and repeats the process for $R_{3}$,\cite{Ling2012} as shown in Figure 3. The TLS/IP connections remain open, so the returned information travels back up the circuit to the end user.

@@

% http://security.stackexchange.com/questions/8343/what-key-exchange-mechanism-should-be-used-in-tls
% https://en.wikipedia.org/wiki/Comparison_of_TLS_implementations
% https://www.ipa.go.jp/security/rfc/RFC5246-ACJA.html

Encryption is a necessary to achieve privacy both inside and outside the Tor network. Traffic passing between nodes must be secured from outsiders to prevent adversaries from following the entire circuit. Layers of encryption also prevent compromised nodes from observing the traffic in cleartext. The exit node is especially important; encrypted connections are often established the recipient outside Tor so that the exit node cannot observe the intended message.

Within the network, nodes talk to each other via the Transport Security Layer (TLS) protocol. During circuit construction, the client incrementally performs a handshake with each relay in turn, establishing an agreement over the encryption key and specific symmetric cipher. There are several mechanisms by which this is done, most of which use the Diffie-Hellman-Merkle (DH) protocol for key exchange. The ephemeral version of DH provides perfect forward secrecy by generating a new session key for every handshake. The secret keys for DH ($a$ and $b$) are not stored, preventing attackers from decrypting prior communication even if the relay is later compromised. Authentication of communication is achieved through RSA or elliptic curve public keys, with the SHA-1 serving as the hash function for integrity verification.

Tor users typically use the Tor Browser Bundle, (TBB) a custom build of Mozilla Firefox with a focus on security and privacy. The TBB not only provides special handling of client-side scripts such as Javascript, but also offers the HTTPS Everywhere extension, which uses regular expressions to rewrite HTTP web requests into HTTPS whenever possible. Thus, if the web server is capable of handling SSL or TLS connections, HTTP communications will be encrypted to them. If this is the case, the TBB performs a TLS handshake with the web server, but the exchange happens through the Tor circuit. This provides the final layer of encryption to the outside.

In September 2013, Robert Graham of Errata Security performed a small study on what cryptography methods Tor primarily used. His exit node analyzed 22,920 incoming connections found that 89.9\% of the circuits agreed to use the Advanced Encryption Standard (AES) block cipher in cipher-block chaining (CBC) mode. This is the most common mode for AES, and allows for parallel decryption of the data blocks. The other 10.1\% of the circuits relied upon three rounds of the Data Encryption Standard (triple DES) cipher for encryption. Furthermore, 75.7\% of the circuits used elliptic-curve DH, with the remaining 22.3\% relying upon traditional RSA DH.\cite{Graham2013} Both protocols are discussed below.

@@

RSA is an algorithm for public-key cryptography. Its security is based on the infeasibility of factoring the product of two large primes. RSA, like all other public-key cryptography algorithms, relies upon two keys: one public and the other private. The public key may be published and is used for encryption and for the verification of digital signatures. The private key is used for decryption and the generation of digital signatures. Thus, only the owner of the private key can decrypt incoming messages, and only they can digitally sign outbound messages. These properties make RSA and other public-key algorithms extremely powerful as they can provide authenticity, integrity, and privacy of communications between two parties.

However, RSA operations are computationally expensive, and RSA only provides one-way authentication and privacy. Both parties must have RSA keys in order to achieve private two-way authenticated communication. This situation is unlikely and often infeasible to implement, so RSA is used by TLS in conjunction with faster symmetric-key encryption algorithms.

Tor version 2.3.x and previous primarily rely upon TLS\_DHE for the key exchange mechanism. In this protocol, Bob replies to Alice with a dynamically-generated (ephemeral) DH key and signs this with his private RSA key. Alice can then confirm the digital signature to verify the authenticity of the communication. Thus the client can prove the authenticity of replies from Tor relays in the circuit or with the end web server.

@@

A smaller key size is one of the most significant benefits introduced by ECC. Current NIST recommendations state that a key size of 160 bits for ECC offers a similar level of security to 1024 bits of RSA and Diffie-Hellman-Merkle. Likewise, 224 bits for ECC is analogous to 2048 bits of RSA/DH. It should be noted that the required key sizes for ECC increases significantly slower than the key sizes for RSA/DH. Thus ECC offers more security per increase in key size than for RSA. The smaller key size also directly correlates to an increase in computational efficiency; as the bit size increases, the speed difference between RSA/DH and ECC operations grows superlinearly.\cite{CaseForECC}

Tor is currently undergoing a transition from RSA-based to elliptic-curve-based TLS. Tor 2.4.x introduced TLS\_ECDHE, which uses an elliptic-curve variant of DH and it became the preferred key exchange protocol. 2.4.x relays also offer both an RSA and elliptic curve public key for authentication purposes in TLS. The transition to ECC reduces computational demand and is believe to provide stronger security.

@@

Once the TLS handshake and DH key exchanges complete, both parties use the generated session key and turn to symmetric-key encryption for hiding of data. Common symmetric-key algorithms include Data Encryption Standard, Advanced Encryption Standard, and RC4.

@@

% -------------------------------------------------------------------------------
